Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2024-01-02 demystify.tex
updates

\begin{table}
  \centering
  \small
  \caption{Top 50 CS PhD programs in the U.S. (CSRankings, June 2023). \red{$^*$} indicates that the university has \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{Vietnamese prof.} that can advise CS PhD students.}\label{tab:ranking}
  \begin{tabular}{rl|rl}
    \toprule
    1 & Carnegie Mellon & 26 & Univ. of California - Irvine \\
    2 & Univ. of Illinois at Urbana-Champaign\red{$^*$}  & 27 &  Duke University \\
    3 & Univ. of California-San Diego & 28 & Rutgers University\red{$^*$} \\
    4 & MIT & 29 & Univ. of California - Riverside\\
    5 & Georgia Institute of Technology         & 30 & Northwestern University\\
    6 & Stanford University& 31 & Pennsylvania State University  \\
    7 & University of Michigan - Ann Arbor\red{$^*$}   & 32& George Mason University\red{$^*$}\\  
    8 & University of Washington      &33 &  Harvard University \\
    9 &  Univ. of California - Berkeley  &34&  Univ. of California - Santa Cruz \\
    10 & Cornell University  & 35 &  Yale University \\
    11 & University of Maryland - College Park &  36& Brown University \\ 
    12 & Northeastern University\red{$^*$} &37&  Ohio State University\\
    13 & University of Wisconsin - Madison\red{$^*$}  &38& Texas A\&M University\red{$^*$} \\
    14 & Columbia University   &39 & Boston University  \\
    15 &   Purdue University  &40& North Carolina State University\\\  
    16 & University of Texas at Austin   &41 & University of Utah \\
    17 & University of Pennsylvania\red{$^*$} &42 & University at Buffalo\red{$^*$}\\
    18 & Princeton University  & 43& Rice University\\
    19 & University of Massachusetts-Amherst\red{$^*$} & 44&  University of Colorado-Boulder \\
    20 &  New York University  &45& University of Illinois at Chicago  \\
    21 & Univ. of California - Los Angeles &46& Virginia Tech\red{$^*$}  \\
    22 & University of Southern California &47&  Arizona State University\red{$^*$} \\
    23 & Stony Brook University\red{$^*$} &48&University of Minnesota \\
    24 & University of Chicago &49& University of Virginia \\
    25 & Univ. of California - Santa Barbara &50& University of North Carolina\red{$^*$} \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \centering
  \small
  \caption{Top 50 CS PhD programs in the U.S. (CSRankings, June 2023). \red{$^*$} indicates that the university has \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{Vietnamese prof.} that can advise CS PhD students.}\label{tab:ranking}
  \begin{tabular}{rl|rl}
    \toprule
    1 & Carnegie Mellon & 26 & Univ. of California - Irvine \\
    2 & Univ. of Illinois at Urbana-Champaign\red{$^*$}  & 27 &  Duke University \\
    3 & Univ. of California-San Diego & 28 & Rutgers University\red{$^*$} \\
    4 & Georgia Institute of Technology & 29 & Univ. of California - Riverside\\
    4 & MIT         & 30 & Northwestern University\\
    6 & Univ. of California - Berkeley& 31 & Pennsylvania State University  \\
    7 & University of Michigan - Ann Arbor\red{$^*$}   & 32& George Mason University\red{$^*$}\\  
    8 & University of Washington      &33 &  Harvard University \\
    9 &  Stanford University  &34&  Univ. of California - Santa Cruz \\
    10 & Cornell University  & 35 &  Yale University \\
    11 & University of Maryland - College Park &  36& Brown University \\ 
    12 & Northeastern University\red{$^*$} &37&  Ohio State University\\
    13 & University of Wisconsin - Madison\red{$^*$}  &38& Texas A\&M University\red{$^*$} \\
    13 & Purdue University  &39 & Boston University  \\
    15 & University of Texas at Austin &40& North Carolina State University\\\  
    16 & University of Pennsylvania &41 & University of Utah \\
    17 & Columbia University \red{$^*$} &42 & University at Buffalo\red{$^*$}\\
    18 & Princeton University  & 43& Rice University\\
    19 & New York University  & 44&  University of Colorado-Boulder \\
    20 &  University of Massachusetts-Amherst\red{$^*$} &45& University of Illinois at Chicago  \\
    21 & Univ. of California - Los Angeles &46& Virginia Tech\red{$^*$}  \\
    22 & University of Southern California &47&  Arizona State University\red{$^*$} \\
    23 & Stony Brook University\red{$^*$} &48&University of Minnesota \\
    24 & University of Chicago &49& University of Virginia \\
    25 & Univ. of California - Santa Barbara &50& University of North Carolina\red{$^*$} \\
    \bottomrule
  \end{tabular}
\end{table}
